Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-03-04 ms.tex
Fixing "\densSlope"
log-normal

The bottom panel of Figure~\ref{fig:bh_growth} shows the SMBH growth
time, $t_{\rm grow} = M_{\bullet}/\dot{M}$, for each accretion rate
shown in the top panel.  For black holes accreting steadily given the
stellar wind heating associated with the average star formation
history of their galaxies, we see that $t_{\rm grow}$ exceeds the
Hubble time by 1-3 orders of magnitude across all black hole masses.
Steady accretion therefore cannot explain the growth of low mass black
holes, a fact which is not surprising given that approximately half of
this growth occurs in AGN radiating within 10 per cent of their
Eddington rate (\citealt{Heckman+04}).  Such high accretion rates
likely instead require an source of gas external to the nuclear
region, triggered either by galaxy mergers associated with the
hierachical growth of structure or thermal instabilities on larger,
galactic scales (e.g.~\citealt{Ciotti+10}).  That the growth time
associated with thermally-unstable accretion (yellow line) exceeds the
Hubble time across all SMBH masses highlights the fact that signifcant
black hole growth in the local universe cannot result from
thermally-stable steady accretion.

>>>>

The bottom panel of Figure~\ref{fig:bh_growth} shows the SMBH growth
time, $t_{\rm grow} = M_{\bullet}/\dot{M}$, for each accretion rate
shown in the top panel.  For black holes accreting steadily given the
stellar wind heating associated with the average star formation
history of their galaxies, we see that $t_{\rm grow}$ exceeds the
Hubble time by 1-3 orders of magnitude across all black hole masses.
Steady accretion therefore cannot explain the growth of low mass black
holes, a fact which is not surprising given that approximately half of
this growth occurs in AGN radiating within 10 per cent of their
Eddington rate (\citealt{Heckman+04}).  Such high accretion rates
likely instead require an source of gas external to the nuclear
region, triggered either by galaxy mergers associated with the
hierachical growth of structure or thermal instabilities on larger,
galactic scales (e.g.~\citealt{Ciotti+10}).

\citet{Kauffmann&Heckman09} find that the growth of low mass black
holes is dominated by young stellar bulges which have a log normal
distribution of Eddington ratios peaked at $\Mdot/\MdotEdd\sim
0.01$. The distribution is insensitive to galaxy properties which
suggestes that it is set by feedback from the black hole rather than
from the gas supply in the nucleus.

That the growth time associated with thermally-unstable accretion
(yellow line) exceeds the Hubble time across all SMBH masses
highlights the fact that signifcant black hole growth in the local
universe cannot result from thermally-stable steady accretion of gas
lost from the surrounding stellar population.
